Textmining in Economics

### 2017-10-14 textm.Rmd
new

```{r, eval=FALSE}
library(lda)

@@

```{r, eval=FALSE}
ldaModel <- lda.collapsed.gibbs.sampler(corpusLDA$documents,K=2,vocab=corpusLDA$vocab,burnin=9999,num.iterations=100000,alpha=0.8,eta=0.1)

>>>>

```{r, eval=FALSE, include=FALSE}
library(lda)

@@

```{r, eval=FALSE, include=FALSE}
ldaModel <- lda.collapsed.gibbs.sampler(corpusLDA$documents,K=2,vocab=corpusLDA$vocab,burnin=9999,num.iterations=100000,alpha=0.8,eta=0.1)
